Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-01 paper/Draft.tex
Improved the formatting of figures with only IR left.

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1in,right=1in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{threeparttable}

@@

	The paper is organized as followed. Section \label{theory} first sets up a common framework in which testable various theories can be compared. Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments. Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time series regressions that test the implications of these theories.   Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.  Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.

@@

	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories. Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.  And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=16cm]{figures/ir_popseni.png} 
			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e. $\omega_t=1$. For NI, public and private signals’ variance is equal to long-run variance of $y$, i.e. $\sigma_\epsilon = \sigma_\xi = \sigma_\xi $. For SE, $\lambda = 0.75$.  }
		\caption{Impulse responses of population moments to a shock to inflation}
		\label{ir_pop}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=13cm]{figures/rigidity.png} \\
		{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI. Rigidity from NI are plotted for three values of noisiness of signals, i.e. 0.1, 1 and 10 times of the unconditional variance of $y$. }
		\caption{Rigidity from Two Models}
		\label{rigidity}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
		\includegraphics[width=4.5cm]{figures/Inf1yf_PCE_varSPFPCEQ.png}
		\includegraphics[width=4.5cm]{figures/Inf1yf_CPIAU_varSCEM.png}\\
		\smallskip
		\includegraphics[width=4.5cm]{figures/SPFCPI_FE_varSPFCPIQ.png}
		\includegraphics[width=4.5cm]{figures/SPFPCE_FE_varSPFPCEQ.png}
		\includegraphics[width=4.5cm]{figures/SCE_FE_varSCEM.png}\\
		\smallskip	
		\includegraphics[width=4.5cm]{figures/CPI_disg_varSPFCPIQ.png}
		\includegraphics[width=4.5cm]{figures/PCE_disg_varSPFPCEQ.png}
		\includegraphics[width=4.5cm]{figures/Q9_disg_varSCEM.png}\\
		{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62. }
		\caption{Unceratinty and Other Moments}
		\label{UnceratitnyOtherMoments}
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png} \\
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}\\
		\caption{Dispersion in Mean Forecast and Unceratinty }
		\label{IQR_Unceratitny}
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  \\
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  \\
		\smallskip
		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  \\
		\caption{Distribution of Mean Forecast and Uncertainty }
		\label{Unceratitny_Histogram}
	\end{figure}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  \\
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png}  \\
		\caption{Distribution of Revision in Forecasts and Uncertainty}
		\label{RevisionHist}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=12cm]{figures/inf_shocksQ.png}
		\caption{ Shocks to Inflation}
		\label{Inflationshocks}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
		\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_before2007.png} \\
		\smallskip
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_before2007.png} \\
		\smallskip
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
		\label{ReplicateCoibionBefore2007}
	\end{figure}

>>>>

\documentclass[]{article}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1in,right=1in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=blue,      
	urlcolor=blue,
	citecolor=blue
}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

@@

	The paper is organized as followed. Section \ref{theory} first sets up a common framework in which testable various theories can be compared. Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments. Section \ref{empirical} discusses the survey data used for this paper and presents both the stylized patterns and time series regressions that test the implications of these theories.   Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.  Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.

@@

	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories. Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to one unconditional standard deviation of $y$.  And the $\lambda$ is set to be $0.75$, implying on average an update interval of four quarters.

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\textwidth]{figures/ir_popseni.png} 
		\begin{flushleft}
			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e. $\omega_t=1$. For NI, public and private signals’ variance is equal to long-run variance of $y$, i.e. $\sigma_\epsilon = \sigma_\xi = \sigma_\xi $. For SE, $\lambda = 0.25$.  }
		\end{flushleft}
		\caption{Impulse responses of population moments to a shock to inflation}
		\label{ir_pop}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\textwidth]{figures/rigidity.png} 
		\begin{flushleft}
			{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI. Rigidity from NI are plotted for three values of noisiness of signals, i.e. 0.1, 1 and 10 times of the unconditional variance of $y$. }
		\end{flushleft}
		\caption{Rigidity from Two Models}
		\label{rigidity}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Realized Inflation and Uncertainty}
			\label{InfVar}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
		\end{subfigure}
	    \vspace{1em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Forecast Errors and Uncertainty}
			\label{FEVar}
			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_FE_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_FE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SCE_FE_varSCEM.png}
		\end{subfigure}
	 \vspace{0.5em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Disagreements and Uncertainty}
			\label{DisgVar}
			\includegraphics[width=0.3\textwidth]{figures/CPI_disg_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/PCE_disg_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
		\end{subfigure}
		\\
		\begin{flushleft}
			{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62. }
		\end{flushleft}
		\caption{Uncertainty and Other Moments}
		\label{UnceratitnyOtherMoments}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Mean Forecasts}
		\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
		\end{subfigure}
	    \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
		\centering 
		\caption{Uncertainty}
		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}
		\end{subfigure}
		\caption{Dispersion of Mean Forecasts and Unceratinty }
		\label{IQR_Unceratitny}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Revision in Mean Forecasts}
		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
		\end{subfigure}
	   \hfill 
	  	\begin{subfigure}[b]{0.5\textwidth}
	  	\caption{Revision in Uncertainty}
		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  
		\end{subfigure}
		\caption{Distribution of Mean Forecast and Uncertainty }
		\label{Unceratitny_Histogram}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
		\end{subfigure}
		   \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png} 
		\end{subfigure}
		\caption{Distribution of Revision in Forecasts and Uncertainty}
		\label{RevisionHist}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\textwidth]{figures/inf_shocksQ.png}
			\begin{flushleft}
			{\footnotesize Note: all the shocks are normalized by their sample standard deviation. Technology shock is idetified by long-run restriction of structural VAR with labor productivity, hours and inflation. Oil shock is defined as the max \{0, the largest increase of oil price over the past 12 months.\} }
		\end{flushleft}
		\caption{ Shocks to Inflation}
		\label{Inflationshocks}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
				\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
					\smallskip
				\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
		\end{subfigure}	
	    \hfill 
	    \begin{subfigure}[b]{0.5\textwidth}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\end{subfigure}
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
		\label{ReplicateCoibionBefore2007}
	\end{figure}
